BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-07-19 manuscript/BarnebyLives -COPY2 ACTUALLY CLEAN.rmd

data1 <- data |>
  sf::st_drop_geometry() |>
  split_scientificName(sciName_col = 'Scientific_name')

  # for these records, we want to retain the originally entered information 
  mutate(
    POW_Family = if_else(Collection_number %in% c(2435, 2517), 'Ranunculaceae', POW_Family)), 
    POW_Genus

  ) |>

  select(-SpellCk.gGRP, -Match, -SpellCk.taxon_rank, 
        -Infrarank, -Infraspecies, -Binomial_authority, -Infraspecific_authority, -Family) |>
  rename(Full_name = SpellCk.taxon_name,
         Genus = SpellCk.genus, 
         Epithet = SpellCk.species, 
         Binomial_authority = POW_Binom_authority, 
         Infraspecific_authority = POW_Infra_authority,
         Infrarank = SpellCk.infraspecific_rank, 
         Infraspecies = SpellCk.infraspecies,
         Family = POW_Family) %>% 
  mutate(
    Slope = slope, 
    Aspect = aspect
  ) |>
  unite(Name_authority, 
        Genus, Epithet, Binomial_authority, Infrarank, Infraspecies, Infraspecific_authority,
        remove = F, na.rm = T, sep = ' ') |>
  sf::st_drop_geometry()

@@

```{r Create Labels, eval = F}
processed <- read.csv('data/processed/cleaned_data-problemchildren.csv.csv') %>% 
  mutate(UNIQUEID = paste0(Primary_Collector, Collection_number), 
         Coordinate_Uncertainty = '+/- 5m') %>% 
  filter(Collection_number != 'sine non') %>% 
  data.frame()

processed <- data.frame( apply(processed, 2, as.character) )
processed <- mutate(processed, Collection_number = as.numeric(Collection_number))

@@

saveRDS(raw_lab_time, file = 'data/processed/time_label_gen')

>>>>

data <- data |>
  sf::st_drop_geometry() |>
  split_scientificName(sciName_col = 'Scientific_name') |>

  # for these records, we want to retain the originally entered information 
  mutate(
    POW_Family = if_else(Collection_number %in% c(2435, 2517), 'Ranunculaceae', POW_Family),
    POW_Genus = if_else(Collection_number %in% original_names, Genus, POW_Genus),
    POW_Epithet = if_else(Collection_number %in% original_names, Epithet, POW_Epithet),
  ) |> 
  select(-SpellCk.gGRP, -Match, -SpellCk.taxon_rank, -Genus, -Epithet,
        -Infrarank, -Infraspecies, -Binomial_authority, -Infraspecific_authority, -Family) |>
  rename(Full_name = POW_Full_name,
         Genus = POW_Genus, 
         Epithet = POW_Epithet, 
         Binomial_authority = POW_Binom_authority, 
         Infraspecific_authority = POW_Infra_authority,
         Infrarank = SpellCk.infraspecific_rank, 
         Infraspecies = SpellCk.infraspecies,
         Family = POW_Family) %>% 
  mutate(
    Slope = slope, 
    Aspect = aspect
  ) |>
  unite(Name_authority, 
        Genus, Epithet, Binomial_authority, Infrarank, Infraspecies, Infraspecific_authority,
        remove = F, na.rm = T, sep = ' ') |>
  sf::st_drop_geometry()

@@

```{r Create Labels, eval = F}
processed <- read.csv('data/processed/cleaned_data-problemchildren.csv') %>% 
  mutate(UNIQUEID = paste0(Primary_Collector, Collection_number), 
         Coordinate_Uncertainty = '+/- 5m') %>% 
  filter(Collection_number != 'sine non') %>% 
  data.frame()

processed <- data.frame(apply(processed, 2, as.character))
processed <- mutate(processed, Collection_number = as.numeric(Collection_number))

@@
